\documentclass[a4paper,12pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS}
\usepackage{ragged2e}
\usepackage{fourier}
\usepackage{tikz} 
\usetikzlibrary{chains,shapes.arrows,fit}

\definecolor{arrowcolor}{RGB}{201,216,232}% color for the arrow filling
\definecolor{circlecolor}{RGB}{79,129,189}% color for the inner circles filling
\colorlet{textcolor}{white}% color for the text inside the circles
\colorlet{bordercolor}{white}% color for the outer border of circles

\pgfdeclarelayer{background}
\pgfsetlayers{background,main}

\newcounter{task}

\newlength\taskwidth% width of the box for the task description
\newlength\taskvsep% vertical distance between the task description and arrow

\setlength\taskwidth{2.5cm}
\setlength\taskvsep{17pt}

\def\taskpos{}
\def\taskanchor{}

\newcommand\task[1]{%
  {\parbox[t]{\taskwidth}{\scriptsize\Centering#1}}}

\tikzset{
inner/.style={
  on chain,
  circle,
  inner sep=2pt,
  fill=circlecolor,
  line width=1.5pt,
  draw=bordercolor,
  text width=1.2em,
  align=center,
  text height=1.25ex,
  text depth=0ex
},
on grid
}

\newcommand\Task[2][]{%
\node[inner xsep=0pt] (c1) {\phantom{A}};
\stepcounter{task}
\ifodd\thetask\relax
  \renewcommand\taskpos{\taskvsep}\renewcommand\taskanchor{south}
\else
  \renewcommand\taskpos{-\taskvsep}\renewcommand\taskanchor{north}
\fi
\node[inner,font=\footnotesize\sffamily\color{textcolor}]    
  (c\the\numexpr\value{task}+1\relax) {#1};
\node[anchor=\taskanchor,yshift=\taskpos] 
  at (c\the\numexpr\value{task}+1\relax) {\task{#2}};
}

\newcommand\drawarrow{% the arrow is placed in the background layer 
                                                     % after the node for the tasks have been placed
\ifnum\thetask=0\relax
  \node[on chain] (c1) {}; % if no \Task command is used, the arrow will be drawn
\fi
\node[on chain] (f) {};
\begin{pgfonlayer}{background}
\node[
  inner sep=10pt,
  single arrow,
  single arrow head extend=0.8cm,
  draw=none,
  fill=arrowcolor,
  fit= (c1) (f)
] (arrow) {};
\fill[white] % the decoration at the tail of the arrow
  (arrow.before tail) -- (c1|-arrow.west) -- (arrow.after tail) -- cycle;
\end{pgfonlayer}
}

\newenvironment{timeline}[1][node distance=.6\taskwidth]
  {\par\noindent\begin{tikzpicture}[start chain,#1]}
  {\drawarrow\end{tikzpicture}\par}


\begin{document}


\begin{mcdletter}[Subcontract Release Note: BMS]

We attach the following documentation for the enquiry.

\begin{enumerate}    

\item Full Mechanical and Electrical specifications to which the Subcontractor will need to comply fully.
\item List of Suppliers.
\item Compliance Statement.
\end{enumerate}

Please note that the following must be included fully with the Supplier's offer.

\begin{enumerate}
\item Supply and installation of all equipment and detail design and Engineering of all services related to the Building Management System.

\item Subcontractor to allocate full-time staff on-site for the preparation of drawings and submittals as required by the Contract. During installation subcontractor is expected to installl all the equiment provided in its Contract. HLS will provide only power to the subcontarctor's equipment and terminate. Wiring from DDC panels and from sensors to DDC panels or between DDC panels by Subcontractor. All containment will be provided by the HLS/DS JV.

\item Operations and Maintenance Manuals to be delivered at the same time as the Equipment or earlier and to comply with the Contract Requirements in terms of formats and approvals.

\item Spare Parts as per specification to be quoted and a separate price as per manufacturer's recommendations.

\item Warranty as per Contract Conditions of 400 days from Handover to Owner.

\item Commissioning of equipment including progressive commissioning as systems are completed.
\end{enumerate}

Please ensure that all Suppliers complete the Compliance Statement and that these are sent to us together with all relevant details for our evaluation and approval. Preference will be given to Suppliers providing full information/submittals at the quotation stage. Any Supplier not completing the Compliance Statement will summarily be excluded from our evaluation.
\setlength\taskwidth{2.6cm}
\begin{timeline}
\Task[1]{Release Order\\ 21/09/2013}
\Task[2]{Quotations from vendors \\ 10/10/2013}
\Task[3]{Financial Evaluation \\ 3/10/2013}
\Task[4]{Technical Evaluation \\ 7/10/2013}
\Task[5]{Submittal Preparation \\ 17/10/2013}
\Task[6]{Submittal \\ 18/10/2013}
\Task[7]{Approval \\ 3/11/2013}
\Task[8]{Order\\ 5/11/2013}
\Task[9]{Delivery\\28 Feb 2014}
\end{timeline}


\end{mcdletter}
\end{document}