\documentclass[a4paper,11pt,oneside]{article}
\usepackage[left=2.5cm,right=2.0cm,top=2cm,bottom=2.0cm]{geometry}
\usepackage{HS,lipsum}
\usepackage{graphicx}
\usepackage{lastpage}


\begin{document}

\Date 

\OurRef{HS-118/HLG/YL/mr/1002}

\TO

\RE{HEE 901B/1.3/ZH/GK/17045 dated 1 aug 2013}

\setlength{\parskip}{\baselineskip}

We refer to DIWAN's letter Ref: DCC/DIWAN/Hlg/IIIA/bc/L0420 dated 8 Sep 2013. We note that the letter bears the initials of the Owner's MEP Projects Director and the contents of which the Engineer has adopted \textit{carte blanche}. At the onset we reject the contents of the letter outright. We expect the Engineer---being the gentleman he is---to refrain from allowing such correspondence to bear his signature, especially if they are directed towards persons rather than responding to issues and providing constructive resolutions. 

The author of the letter states: \textit{It is not surprising that the Contractor \& their MEP Sub-Contractor is oblivious \& ignorant of Engineer's instruction no. 295 \ldots.} For the record the MEP Sub-Contractor is not only not ignorant of this instruction, but is also conversant with the effects of all Engineer's Instructions issued and their negative and disruptive effects on the Project. For the record we attach graphical representation for same. 

Also for the record, we confirm that works within Dragoni's scope of works are outside our scope of co-ordination and any co-ordination is carried out  by the Engineer. We are unable to install the meter as per approved Shop Drawing HEE 901/EPO/M-PL/L1-0J Rev 5, as Dragoni deviated from the plans.

We notify you that we are unable to complete the installation unless an Engineer's Instruction is issued and assurances are given that any monetary claims will be reviewed fairly. Upon receipt of such instructions we notify you that the said meter will be installed according to the terms of the original instruction item c) \textit{The Contractor is informed that the Engineer will accept 'Substantial Completion' without the works instructed under this EI being complete.} 

We once again urge the Engineer to review letters sent to the Contractor carefully and to avoid allowing person's in the Owner's Organization to hijack its role. We reserve all our rights to seek suitable redress according to the Qatari Civil Law against any Organizations and individuals that slander the good name of our Company and that of its subcontractors.






\signature

\end{document}